---
title: "TFM-1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(FirebrowseR)
```

##PRAD:
Donwloading the dataset:
```{bash eval=FALSE, include=FALSE}
wget http://gdac.broadinstitute.org/runs/stddata__2016_01_28/data/PRAD/20160128/gdac.broadinstitute.org_PRAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz
```

```{bash}
ls -larth
tar xzvf gdac.broadinstitute.org_PRAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz 
head gdac.broadinstitute.org_PRAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/PRAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt | cut -f1
```
Incorporing the dataset to R:
```{r}
PRAD.data<-read.delim("~/Documentos/TFM/gdac.broadinstitute.org_PRAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/PRAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt")
head(PRAD.data)
PRAD.data$Hybridization.REF
```


##BREAST:
Donwloading the dataset:
```{bash eval=FALSE, include=FALSE}
wget gdac.broadinstitute.org/runs/stddata__2016_01_28/data/BRCA/20160128/gdac.broadinstitute.org_BRCA.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz
```

```{bash}
ls -larth
tar xzvf gdac.broadinstitute.org_BRCA.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz 
head gdac.broadinstitute.org_BRCA.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/BRCA.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt| cut -f1
```
```{bash}
head gdac.broadinstitute.org_BRCA.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/BRCA.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt | cut -f1
```
Incorporing the dataset to R:
```{r}
 BRCA.data<-read.delim("~/Documentos/TFM/gdac.broadinstitute.org_BRCA.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/BRCA.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt")
head(BRCA.data)
```

##COAD:
Donwloading the dataset:
```{bash eval=FALSE, include=FALSE}
wget gdac.broadinstitute.org/runs/stddata__2016_01_28/data/COAD/20160128/gdac.broadinstitute.org_COAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz
```

```{bash}
ls -larth
tar xzvf gdac.broadinstitute.org_COAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz 
head gdac.broadinstitute.org_COAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/COAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt| cut -f1
```

```{bash}
head gdac.broadinstitute.org_COAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/COAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt | cut -f1
```
Incorporing the dataset to R:
```{r}
 COAD.data<-read.delim("~/Documentos/TFM/gdac.broadinstitute.org_COAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/COAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt")
head(COAD.data)
```

##LUAD:
Donwloading the dataset:
```{bash eval=FALSE, include=FALSE}
wget gdac.broadinstitute.org/runs/stddata__2016_01_28/data/LUAD/20160128/gdac.broadinstitute.org_LUAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz
```

```{bash}
ls -larth
tar xzvf gdac.broadinstitute.org_LUAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0.tar.gz 
head gdac.broadinstitute.org_LUAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/LUAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt| cut -f1
```

```{bash}
head gdac.broadinstitute.org_LUAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/LUAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt | cut -f1
```
Incorporing the dataset to R:
```{r}
 LUAD.data<-read.delim("~/Documentos/TFM/gdac.broadinstitute.org_LUAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2016012800.0.0/LUAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt")
head(LUAD.data)
```

###First look:

A quick look into the the dimension of the dataset, in the rows we have the genes (that`s why all the dataset have the same rows) and in the columns we have our amount of pacients:
```{r}
dim(BRCA.data)
dim(COAD.data)
dim(LUAD.data)
dim(PRAD.data)
```

Those all genes we select only a few (transcript factors only)

Preparation of TF lists:
```{r}
uscs.list<-read.delim("~/Documentos/TFM/uscs_list", header = FALSE)
uscs.list<-uscs.list[-1,3:4]
colnames(uscs.list)<- c("Cell Line", "Factor")
head(uscs.list)
uscs.list[!apply(uscs.list == "", 1, all),]
uscs.list.factors<-as.data.frame(unique(uscs.list[,2]))
uscs.list.factors<-as.data.frame(uscs.list.factors[-1, ])
```

```{r}
uniprot.list <- read.delim("~/Documentos/TFM/uniprot_list.tab")
uniprot.list.factors<-as.data.frame(unique(uniprot.list[,2]))
```

